---
title: "report"
author: "Marta Ilundain"
date: "17/3/2021"
output: pdf_document
params: 
  method: 'lda'
  trainpercent: 0.75
  randomseed: 1
---

```{r include=FALSE}
library(devtools)
library(usethis)
library(ggplot2)

library(kaggler)
kaggler::kgl_auth(username="martailundain",key="55489399e4f868af9b80e535ef1ab841")

library(shiny)
library(shinythemes)
require(shinyjs)
require(summarytools)
```

# INTRODUCTION

This report has been created using a shiny app and then clicking in ``Generate report``. In this work we can see the performance of some statistical learning tools in a wine dataset. 

# PRE PROCESS AND ANALYSIS OF THE DATA

We load the dataset:

```{r}
winedata <- kgl_datasets_download(owner_dataset = "rajyellow46/wine-quality", 
                              fileName = "winequalityN.csv")

#Preprocess of the data

wine = na.omit(winedata)
wine$type = as.factor(wine$type)
wine[,7] = log(wine[,7])
colnames(wine)[7] <- "log_free.sulfur.dioxide"
wine[,8] = log(wine[,8])
colnames(wine)[8] <- "log_total.sulfur.dioxide"
```

Initially, this data set consisted of 6497 red and white variants of the Portuguese "Vinho Verde" wine. After making a summary of the data, we observed that it contained some missing values, but since there were not so many, we used the ``na.omit`` command. Thus, we have worked with a data set of 6463 wines and 13 variables. Let's see the definition of each variable:

- Type: it can be red or white wine. We have that approximately 75$\%$ of all the wines are white.
- Fixed acidity: most acids involved with wine or fixed or nonvolatile (do not evaporate readily)
- Volatile acidity: the amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste.
- Citric acid: found in small quantities, citric acid can add 'freshness' and flavor to wines.
- Residual sugar: the amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with greater than 45 grams/liter are considered sweet.
- Chlorides: the amount of salt in the wine.
- Free sulfur dioxide: the free form of SO2 exists in equilibrium between molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial growth and the oxidation of wine.
- Total sulfur dioxide: amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine.
- Density: the density of water is close to that of water depending on the percent alcohol and sugar content.
- pH: describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale.
- Sulphates: a wine additive which can contribute to sulfur dioxide gas (S02) levels, which acts as an antimicrobial and antioxidant.
- Alcohol: the percent alcohol content of the wine.
- Quality: wine's score (between 0 and 10).

We have seen that variables ``free.sulfur.dioxide" and ``total.sulfur.dioxide" can be easily converted into logarithm in order to obtain a Gaussian distribution, so we have worked with them in logarithm form to obtain better results.

# METHOD

After this preprocess, we use the next three functions to obtain the correspondant results to what we have selected in the Shiny App:

```{r}
setupData <- function(trainpercent, randomseed)
{
  # To make computations reproducible.
  set.seed(randomseed)

  # Partition intro training and testing.
  spl = caret::createDataPartition(wine$type, p = trainpercent, list = FALSE)  # 80% for training
  
  wineTrain = wine[spl,]
  wineTest = wine[-spl,]
  invisible( list(training=wineTrain, testing=wineTest) )
}

generic.fit <- function(method, training, testing)
{
  
  fit <- train(type ~ ., data = training, method=method)
  OutOfSample  <- predict(fit, newdata=testing)
  confusion <- confusionMatrix(testing$type, OutOfSample, positive='white')
  
  invisible( list(fit=fit, confusion=confusion) )
}

# Setup data when the partition or the seed change and use a specified method.
responseRoutine <- function(method, trainpercent, randomseed)
{
  d <- setupData(trainpercent, randomseed)
  fit <- generic.fit(method, d$training, d$testing)
  invisible(fit)
}
```

We have been able to change the random seed, the data partition and the method in which we perform the analysis (the options were ``lda``, ``qda`` and ``rpart`` (decision tree)). Using these, we obtain:

# RESULTS

We obtain the following results using the parameters selected in the App:

```{r}
result = responseRoutine(params$method, params$trainpercent, params$randomseed)
```

We have used the following parameters:

```{r}
# Method used:
params$method
```

```{r}
# Data partition used in training:
params$trainpercent
```

```{r}
# Random seed used:
params$randomseed
```




## Fit of the model:

The first output in the Shiny is the fit of the model, which is:

```{r}
result$fit
```

#Confusion matrix:

We can also study its confusion matrix:

```{r}
result$confusion
```



